### 2017-12-12 External Examination/Response To Referees.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{mathrsfs}
\usepackage[margin=0.9in]{geometry}
\usepackage{url}
\usepackage{enumerate}
\usepackage{dsfont}
\usepackage{hyperref}

\begin{document}
RE: Response to external examination reports for Tianyu Raymond Li's PhD
\\
\\
School of Mathematics and Applied Statistics \\
University of Wollongong \\
Wollongong, New South Wales \\
Australia 2522
\\
\\
5 Dec 2017
\\
\\
Dear A/Prof Adam Rennie,
\\
\\
I would like to thank you once again for taking the time to handle the administrative processes involved with submitting my thesis for external examination and together with my supervisors (Dr Marianito Rodrigo and A/Prof Joanna Goard), sifting through the examination reports and constructing a report for me. 
\\
\\
I have attached below a point-by-point response to each of the external examiner's comments and suggestions. The two examiners were Prof Matt Davison of Western University (Canada) and Dr Jeff Dewynne of University of Oxford (UK). Any changes made to the revised thesis are now in \textcolor{blue}{blue}. I wish to highlight two points from Matt Davison have not been addressed as they were simply statements rather than changes to be made. Those have been omitted.
\\
\\
Kindest regards,
\\
\\
Tianyu Raymond Li
\\
\\
\\
\textcolor{blue}{\textbf{Responses to Prof Matt Davison\\ \\}}
\begin{enumerate}
    \item \textbf{Page 1 first sentence of the last paragraph. I would say we are talking about the Black-Scholes equation here-- it is fairly common usage to reserve the phrase ``Black-Scholes formula'' for expressions like $C(S,t) = SN(d_1) - Ke^{-rt}N(d_2)$.
    \\
    \\}
    The phrase ``Black-Scholes formula'' in this sentence has been changed to read ``Black-Scholes equation'' on pg.~1 of the revised thesis.
     \item \textbf{Page 3 2nd line ``early early"' $\rightarrow$ ``early".
    \\
    \\}
    The extra ``early'' has been removed.
     \item \textbf{Page 12 2nd last line ``directly evaluating of the Inverse Mellin...'' $\rightarrow$ ``directly evaluating the inverse Mellin...''.
    \\
    \\}
    The typo has been fixed on pg.~12 of the revised thesis.
     \item \textbf{Page 20 last line ``Dupre'' $\rightarrow$ ``Dupire''.
    \\
    \\}
    The typo has been fixed.
     \item \textbf{Page 24 2nd last line after eq (2.8) -- I would simplify the sentence ``As aforementioned in the introduction'' to simply read ``As mentioned in the introduction''.
    \\
    \\}
    The sentence now reads ``As mentioned in the introduction'' on pg.~25 of the revised thesis.
      \item \textbf{Page 24 bottom of the page. While I agree that the smooth pasting conditions can arise from a profit maximizing argument, and even how this makes the $V(S^*(t),t) = K - S^*(t)$ half of the smooth pasting condition essential, it is harder to understand why the derivative term of the smooth pasting condition corresponds to maximization. In fact, I prefer to think of the derivative term as arising from the need to have a $\Delta$ of -1 at put exercise to avoid any risk in the hedged porfolio. 
    \\
    \\}
    Additional references have been provided here to reinforce the financial significance of the smooth pasting conditions. A proof has also been cited (please refer to pg.~26 of the revised thesis).

@@

      \item \textbf{Page 25 Line 2, superfluous space between ``formulation'' and the period.
    \\
    \\}
    The unwarranted space has been removed.

      \item \textbf{Page 31 statement of Lemma 3 ``it follows from that'': follows from what?
    \\
    \\}
    This is a typo. It has been changed to read ``it follows that'' on pg.~33 of the revised thesis.
    \item
     \textbf{Page 33 statement of Lemma 8 -- don't italicize ``and''. Line following eq (2.43) -- not sure why some words are italicized here and not others.
    \\
    \\}
    The inconsistent italics have been removed.
    \item \textbf{Page 33/34 Lemma 8 ``defined to be the discretized Black-Scholes kernel (pg 33)''. I don't love this nomenclature as the kernel from Lemma 8 (2.44) seems perfectly continuous to me. Can a different name be found here?
    \\
    \\}
    The reason for the word ``discretized`` is to differentiate it from the expression for the Black-Scholes kernel that corresponds to an asset that pays a continuous dividend yield versus a discrete dividend payment. We believe the expression is suitable as it is and has not been altered.

@@

     \item \textbf{Page 51 -10 lines from the end -- I think you mean ``$H$ functions'' not ``$Hh$ functions''? Of course the link between $H$ functions and $G$ functions and the Mellin transforms is very fundamental.
    \\
    \\}
    This is no typo. We were indeed referring to $Hh$ functions that Kou~\cite{Kou2002,Kou2004} implemented to handle the jump-diffusion dynamics following a double exponential distribution.

     \item \textbf{Page 55 first line of section 4.1.2 ``are in terms of the strike price'' $\rightarrow$ ``are with respect to the strike price''.
    \\
    \\}
    The phrase has been changed to the recommendation on pg.~57 of the revised thesis.

@@

         \item \textbf{Page 63 I feel there are way too many significant figures here.
    \\
    \\}
    The number of significant figures was a by-product of using \emph{format long} in MATLAB (which is what we used to generate our data). Additionally, these results have already been accepted and published. Thus, we will be keeping the data as is.

         \item \textbf{Page 73 last line -- change to: ``is because, upon inversion, this...''.
    \\
    \\}
    The last line has been changed to what was recommended on pg.~75 of the revised thesis.

         \item \textbf{Page 95, line 5 ``was done in [26]" $\rightarrow$ ``was investigated in [26]'' or ``was reported in [26]".
    \\
    \\}
    This has been changed to ``was reported in'' on pg.~97 of the revised thesis.

         \item \textbf{Page 77 5th last line ``instigating'' the properties of the Delta function? Perhaps you mean the properties of the Delta function?
    \\
    \\}
    This has been addressed and changed to ``using the properties of the Delta function'' on pg.~79 of the revised thesis.

@@

			\item{\textbf{Page 73, (5.9): } It might be a good idea to use a different symbol to $\mathscr{J}$, which has already been used earlier.
			\\\\}
			We prefer to leave $\mathscr{J}$ in Eq.~(5.9) as it is for consistency of notation. In any case, we do not use the previous result Eq.~(3.13) here (i.e., different definitions).

			\item{\textbf{Page 74, \S5.1.2: } The ``lemma $n$'', ``Lemma $m$'' problem is particularly bad in this section (there is also an ``eq (3.18)'' on Page 75, whereas you usually write ``Eq.~(m.n)'').
			\\\\}
			The mixture of lowercase and uppercase for the word \emph{lemma} has now been fixed to be consistent along with fixing the outlier ``eq'' to be ``Eq''.

			\item{\textbf{Page 81, 2nd line from the bottom: } I would change ``Similar to how we handled $I_{3,a}$'' to ``Similarly to how we dealt with $I_{3,a}$''.
			\\\\}
			This has been changed on the bottom of pg.~83 of the revised thesis.

			\item{\textbf{Page 84, \S5.1.3:} I think this section could be shortened. It is not really that different to \S5.1.2 and it sort of gives the impression of ``cut and paste''.
			\\\\}
			\S5.1.3 was provided in full to complement \S5.1.2. This is because the formulas grew increasingly complicated that for the benefit of the reader, the details were provided in full so it would not be too overwhelming.

			\item{\textbf{Page 89, under (5.27):} I don't understand what it means for a term to be \emph{mildly involved}.
			\\\\}
			The phrase \emph{mildly involved} has been changed to \emph{rather complicated} on pg.~91 of the revised thesis.
			\item{\textbf{Page 100, \S5.4: } I'm not sure what a ``favourable outcome'' is in the context of a numerical solution, nor am I sure what it means for a numerical result to be ``extremely credible''. I would also dispense with the word (?) ``renownedly''.
			\\\\}
			``Favourable outcome'' is now ``positive results''; ``extremely credible'' is now ``to be accurate'' and the word (?) ``renownedly'' has been removed. These changes can be see on pg.~102 of the revised thesis.

			\item{\textbf{Page 101, (5.45): } But near the exercise boundary the American put is over twice as valuable as the European put. This shows that (5.45) is not always an accurate approximation. Presumably there is some limit in which (5.45) is accurate -- do you know what this limit is?
			\\\\}
			The approximation (5.45) is to simplify the IDE for the free boundary $S^*(t)$ in (5.44). If this assumption was not implemented, then we would have no method of eliminating the $V_a$ term in (5.44). However, the end goal is still an option pricing formula $v_a$ for both an American put and call as seen in (5.17) and (5.29), respectively.

			\item{\textbf{Page 102, under the final displayed equation: } I think ``where we split the integral in $y$ at $y=1$ because this is the value that \emph{would} determine...'' would be more accurate if you changed from \emph{would} to \emph{could}.
			\\\\}
			The word ``would'' is now ``could'' on pg.~104 of the revised thesis.

			\item{\textbf{Page 102: } I am slightly worried when you set $I_2$ to be zero because of cases such as shown in the figure provided. In particular, under your conditions you are always going to have $v_a^{\text{put}}(S^*(t),t) > v_e^{\text{put}}(S^*(t),t)$ and so imagine what happens if you chose $f(y)$ so that $f(y)/y$ has most of its mass near $y=1$.
			\\\\}
			Once again, we wish to reiterate the purpose of setting $I_2$ to be equal to zero is similar to why we used (5.45) to obtain an approximate IDE for the free boundary $S^*(t)$. This to once again remove an additional $v_a$ term that would otherwise make the option pricing formulas implicit and thus inevitably much more complicated.

			\item{\textbf{Page 105, \S5.4.3: } This could be shortened as it is very similar to the main steps given in \S5.4.2
			\\\\}
			The details in \S5.4.3 are provided in its entirety for the benefit of the reader since the equations in this section are quite complicated.

			\item{\textbf{Page 112, 2nd paragraph: } I would change the word \emph{instantiates} to \emph{uses} and eliminate the word \emph{best} from the first sentence.
			\\\\}
			The sentence now reads ``One of the traditional FDMs used in options pricing uses a few change of variables in order to change the PDE (or PIDE) to resemble the typical heat equation.'' on pg.~113 of the revised thesis.

			\item{\textbf{Page 113, bottom line: } I would remove the word \emph{off} so that the sentence reads ``... as the asset price (denoted here by $x$) goes to infinity''.
			\\\\}
			The word \emph{off} has been removed.

			\item{\textbf{Page 120, \S6.2.1, between the final two displayed equations: } I think you mean that you assume that $v_c(y,T_1; K_2, T_2) > K_1$ for all $y > y_c^*$. I'm not sure what purpose the word ``greater'' is serving after $K_1$.
			\\\\}
			The word ``greater'' has been removed.

			\item{\textbf{Page 126, \S6.3: } Much of this has been already said earlier. 
			\\\\}
			We wish to provide the details in full for the benefit of the reader.

			\item{\textbf{Page 126, \S6.3: } I would change the sentence ``The two auxiliary functions in (6.9) are the building blocks for \emph{all possible} financial payoffs in option pricing.'' so that it reads ``The two auxiliary functions in (6.9) are the building blocks for \emph{many} financial payoffs in option pricing.''
			\\\\}
			The sentence now reads  ``The two auxiliary functions in (6.9) are the building blocks for \emph{many} financial payoffs in option pricing.'' on pg.~128 of the revised thesis.

			\item{\textbf{Page 127, \S6.4: } It's not entirely clear how you get from
				$$
					dS_t = [r(t)S_t - D(S_t,t)]dt + \sigma(t) dW_t,
				$$
				to (6.11).\\\\}
			A reference has been provided in the same paragraph right above the displayed equation that leads into the details. We chose to omit them as adding them would not have added much to our content here.

			\item{\textbf{Page 127, \S6,4: } Also you need to say that $q_t < 1$, otherwise you get a negative share price from (6.11). 
			\\\\}
			This assumption was made from the beginning on pg.~130 of the revised thesis with the sentence ``We call the proportion factor $q_d \in [0,1)$.'' which guarantees the factor is strictly less than $1$.

			\item{\textbf{Page 127, \S6.4: } Finally, you need to be a bit careful about saying that the first equation,
							$$
					dS_t = [r(t)S_t - D(S_t,t)]dt + \sigma(t) dW_t,
				$$
				here is ``general''.\\\\}
				The phrase ``in general'' at the beginning of \S6.4 has been removed.

			\item{\textbf{I can't really see why you only do this for a single dividend yield. Certainly if you assume that $r$, $q$ and $\sigma$ are constants then you can use the result that $V(S,t)$ solves the Black-Scholes equation then so too does $V(\lambda S,t)$ for any $\lambda > 0$.}
			\\\\}
			By formulating the argument in this case of using some $\lambda > 0$ to represent the dividend yield, it may be possible, but we did not consider it for the purpose of this thesis as our primary goal was using the Mellin transform to show that an option pricing formula with one discrete dividend yield is able to be solved.
		\end{itemize}
\end{enumerate}

### 2017-12-12 UOW_thesis_template_v2-0/thesis_template/chapters/Intro.tex
:art: only changes left are code and f_n derivatio

	A well-known result for determining the option value is known as the Black-Scholes equation \cite{Black1973}. The Black-Scholes formula is in fact a partial differential equation (PDE) that is also paired with a terminal condition governed by a payoff function. The payoff function merely states what the option's value will be at the expiry date. Typically, this is normally a piecewise linear function of the strike price and the underlying asset (at least in terms of a call and put). One of the most classical methods to solve the Black-Scholes PDE system is to invoke a transformation of variables (further details of this in addition to~\cite{Black1973} can be found in~\cite{Wilmott1995}) that effectively eliminates a few terms and reduces the PDE system to the archetypal heat equation commonly seen in thermodynamics~\cite{cannon1984one}. The motivation for this step is because the heat equation has been studied endlessly in literature and the solution to the PDE system is ascertainable~\cite{Churchill1938}. The original details of~\cite{Black1973} can also be complemented with~\cite{Wilmott1995} for further details and discussion about this derivation. The crux of option valuation is to determine a fair price for the holder to pay the writer to enter into their specified contract. This price is commonly known as the \emph{option premium} (or simply, the premium) that actually signifies the value of the option at time-zero (i.e., starting today).

@@

Frontczak \cite{Frontczak2013} adopted a method of solving the PIDE seen in \cite{Merton1976} using Mellin transforms. He proceeded to re-derive Merton's solution for a European put option via direct inversion. Frontczak's approach of directly evaluating the inverse Mellin integral (i.e., a complex integral) \textcolor{black}{is where the approach could be improved}. Moreover, this process needs to be repeated for different payoffs, making this procedure computationally expensive and tedious.

>>>>

	A well-known result for determining the option value is known as the \textcolor{blue}{Black-Scholes equation} \cite{Black1973}. The Black-Scholes formula is in fact a partial differential equation (PDE) that is also paired with a terminal condition governed by a payoff function. The payoff function merely states what the option's value will be at the expiry date. Typically, this is normally a piecewise linear function of the strike price and the underlying asset (at least in terms of a call and put). One of the most classical methods to solve the Black-Scholes PDE system is to invoke a transformation of variables (further details of this in addition to~\cite{Black1973} can be found in~\cite{Wilmott1995}) that effectively eliminates a few terms and reduces the PDE system to the archetypal heat equation commonly seen in thermodynamics~\cite{cannon1984one}. The motivation for this step is because the heat equation has been studied endlessly in literature and the solution to the PDE system is ascertainable~\cite{Churchill1938}. The original details of~\cite{Black1973} can also be complemented with~\cite{Wilmott1995} for further details and discussion about this derivation. The crux of option valuation is to determine a fair price for the holder to pay the writer to enter into their specified contract. This price is commonly known as the \emph{option premium} (or simply, the premium) that actually signifies the value of the option at time-zero (i.e., starting today).

@@

Frontczak \cite{Frontczak2013} adopted a method of solving the PIDE seen in \cite{Merton1976} using Mellin transforms. He proceeded to re-derive Merton's solution for a European put option via direct inversion. Frontczak's approach of \textcolor{blue}{directly evaluating the inverse Mellin integral (i.e., a complex integral)} \textcolor{black}{is where the approach could be improved}. Moreover, this process needs to be repeated for different payoffs, making this procedure computationally expensive and tedious.

### 2017-12-12 UOW_thesis_template_v2-0/thesis_template/chapters/Preliminaries.tex
:art: only changes left are code and f_n derivatio

We will now construct the foundation needed to tackle the American option pricing problems in this thesis.
As mentioned in the introduction, there are a multitude of ways to formulate the American option pricing problem. \textcolor{blue}{The formulation we will present provides a clear framework for all the possible scenarios that can occur with American options.}

Due to the liberty of being able to exercise the option early, the American option valuation problem involves two unknown functions: the option value itself $V_t$ and
the function $S^*$ which is commonly denoted as the \emph{optimal exercise boundary}~\cite{Kwok2008}. For an American put option, the goal is to ascertain
$v_\text{a}^{\text{put}} =v_\text{a}^{\text{put}}(x,t)$ and $S^* = S^*(t)$ such that
	\begin{enumerate}
			\item $\mathscr{L}v_\text{a}^{\text{put}}(x,t) = 0, \quad x > S^*(t)$,
			\item $v_\text{a}^{\text{put}}(x,t) = K - x, \quad 0 \leq x < S^*(t)$,
	\end{enumerate}
	with a payoff $v_\text{a}^{\text{put}}(x,T) = \max(K-x,0)$. For $x = S^*(t)$, we will introduce continuity conditions which in the literature are regularly referred to as \emph{smooth pasting conditions}. For the American put, these are
		\begin{equation*}
			v_\text{a}^{\text{put}}(S^*(t),t) = K - S^*(t), \quad \fr{\pr v_\text{a}^{\text{put}}}{\pr x}(S^*(t),t) = -1.
		\end{equation*}
	From this formulation, we can view the smooth pasting conditions as reflecting the interests of option holders to maximize their profit. It is a crucial point to note that the delta condition for the American put
	$$
	\fr{\pr v_\text{a}^{\text{put}}}{\pr x}(S^*(t),t) = -1
	$$
is not a by-product of $v_\text{a}^{\text{put}}(S^*(t),t) = K - S^*(t)$. The smooth pasting conditions together are imposed on an American option to ensure the absence of arbitrage opportunities~\cite{Chiarella2014}. The proof for the these smooth pasting conditions for both an American put and call can be found in~\cite{Chin2017}. Although the delta condition is seldom used in deriving the pricing formulae for American options, it is a necessity when solving the above option pricing PDE numerically (e.g., using the method of lines)~\cite{Chiarella2010}. The value of the asset will dictate what choice the holders should make due to the additional unknown $S^*(t)$ as seen above in the problem formulation. For an American put, the interval $0 \leq x < S^*(t)$ is known as the \emph{exercise region} as it is the most optimal time to exercise the option irrespective of time to expiry since the value of the American put is equal to its payoff. In contrast, $x > S^*(t)$ represents the \emph{continuation region} where the American put is worth more than its payoff and thus is more valuable to continue to hold the option. As we have mentioned in the introduction, the position of $S^*(t)$ (which divides the $x$ domain into the exercise and continuation regions) is unknown \emph{a priori} which adds another layer of difficulty to the option pricing problem.

@@

\section{Useful properties of the CDF of a standard normal variable}
\label{subsec:cdfproperties}
Several properties of the \textcolor{blue}{standard} cumulative normal distribution $N$ and its derivative $N'$ will also be required~\cite[pp. 235--239]{Jeff1995}, namely
	\begin{equation}
		\begin{split}
		N(x) = \fr{1}{\sqrt{2\pi}}\int_{-\infty}^x e^{-y^2/2} & \, \d y, \quad %= \fr{1}{2} + \fr{1}{2}\text{erf}\left(\fr{x}{\sqrt{2}}\right) \\
		N(-x) = 1 - N(x), \quad
		N'(x) = \fr{1}{\sqrt{2\pi}}e^{-x^2/2} \label{eqn:Nprime}, \\
		&N(\infty) = 1, \quad N(-\infty) = 0.
		\end{split}
	\end{equation}
We also require the bivariate (standard) normal CDF~\cite{Genz2004}
	\begin{equation}
		\label{eqn:N2}
		N_2(x,y;\rho) = \fr{1}{2\pi\sqrt{1-\rho^2}}\int_{-\infty}^x\int_{-\infty}^y e^{-(u^2-2\rho uv + v^2)/(2(1-\rho^2))} \, \d v \, \d u,
	\end{equation}
where $\rho \in (-1,1)$ . It is not difficult to show that	
	\begin{equation}
		\label{eqn:Nspecial}
		\begin{split}
		&N_2(x,\infty;\rho) = N(x), \quad N_2(\infty,y;\rho) = N(y),\\
		&N_2(x,-\infty;\rho) = N_2(-\infty,y;\rho) = 0, \\
		&N_2(-\infty,\infty;\rho) = N_2(\infty,-\infty;\rho) = 0, \quad N_2(\infty,\infty;\rho) = 1.
		\end{split}
	\end{equation}
\section{Lemmas and corollaries we will need}
The following lemmas and corollaries will also be of great use throughout this thesis:
\subsection{General lemmas}
	\begin{lemma}
		\label{lem:2}
	For $a > 0$ and $b \in \mathbb{R}$, we have
	\begin{equation*}
		\M^{-1}\left\{ e^{-b\xi/a}e^{\xi^2/(2a^2)} \right\} = aN'(a\log x + b).
	\end{equation*}
	\end{lemma}
\begin{proof}
	See Appendix A.1.
\end{proof}
	\begin{lemma}
		\label{lem:1}
		For $a_1, \, a_2 > 0$ and $b_1, \, b_2 \in \mathbb{R}$, we have
			\begin{align*}
				&\int_0^\infty \fr{1}{z}N'(a_1\log z + b_1)N'\left(a_2\log\left( 1/z \right) + b_2 \right) \, \d z =  \fr{1}{\sqrt{a_1^2 + a_2^2}}N'\left( \fr{a_1b_2 + a_2b_1}{\sqrt{a_1^2+a_2^2}} \right).
			\end{align*}
	\end{lemma}
	\begin{proof}
		See Appendix A.2.
	\end{proof}
	\begin{lemma}
		\label{lem:2b}
		For $a_1, \, a_2 > 0$, $b_1, \, b_2 \in \mathbb{R}$, and $c > 0$, it follows that
		\begin{align*}
			&\int_c^\infty \fr{1}{z}N'(a_1\log z + b_1)N'\left(a_2\log\left( 1/z \right) + b_2 \right) \, \d z =  \fr{1}{\sqrt{a_1^2 + a_2^2}}N'\left( \fr{a_1b_2 + a_2b_1}{\sqrt{a_1^2+a_2^2}} \right)N(d),
		\end{align*}
		where
		$$
			d = \sqrt{a_1^2+a_2^2}\left( \log(1/c) + \fr{b_2}{a_2} - \fr{a_1\gamma}{a_1^2+a_2^2} \right), \quad
			\gamma = \fr{a_1b_2}{a_2} + b_1.
		$$
	\end{lemma}
	\begin{proof}
		See Appendix A.3.
	\end{proof}

>>>>

We will now construct the foundation needed to tackle the American option pricing problems in this thesis.
\textcolor{blue}{As mentioned in the introduction}, there are a multitude of ways to formulate the American option pricing problem. \textcolor{blue}{The formulation we will present provides a clear framework for all the possible scenarios that can occur with American options.}

Due to the liberty of being able to exercise the option early, the American option valuation problem involves two unknown functions: the option value itself $V_t$ and
the function $S^*$ which is commonly denoted as the \emph{optimal exercise boundary}~\cite{Kwok2008}. For an American put option, the goal is to ascertain
$v_\text{a}^{\text{put}} =v_\text{a}^{\text{put}}(x,t)$ and $S^* = S^*(t)$ such that
	\begin{enumerate}
			\item $\mathscr{L}v_\text{a}^{\text{put}}(x,t) = 0, \quad x > S^*(t)$,
			\item $v_\text{a}^{\text{put}}(x,t) = K - x, \quad 0 \leq x < S^*(t)$,
	\end{enumerate}
	with a payoff $v_\text{a}^{\text{put}}(x,T) = \max(K-x,0)$. For $x = S^*(t)$, we will introduce continuity conditions which in the literature are regularly referred to as \emph{smooth pasting conditions}. For the American put, these are
		\begin{equation*}
			v_\text{a}^{\text{put}}(S^*(t),t) = K - S^*(t), \quad \fr{\pr v_\text{a}^{\text{put}}}{\pr x}(S^*(t),t) = -1.
		\end{equation*}
	From this formulation, we can view the smooth pasting conditions as reflecting the interests of option holders to maximize their profit. It is a crucial point to note that the delta condition for the American put
	$$
	\fr{\pr v_\text{a}^{\text{put}}}{\pr x}(S^*(t),t) = -1
	$$
is not a by-product of $v_\text{a}^{\text{put}}(S^*(t),t) = K - S^*(t)$. \textcolor{blue}{The smooth pasting conditions together are imposed on an American option to ensure the absence of arbitrage opportunities~\cite{Chiarella2014}. The proof for the these smooth pasting conditions for both an American put and call can be found in~\cite{Chin2017}.} Although the delta condition is seldom used in deriving the pricing formulae for American options, it is a necessity when solving the above option pricing PDE numerically (e.g., using the method of lines)~\cite{Chiarella2010}. The value of the asset will dictate what choice the holders should make due to the additional unknown $S^*(t)$ as seen above in the problem formulation. For an American put, the interval $0 \leq x < S^*(t)$ is known as the \emph{exercise region} as it is the most optimal time to exercise the option irrespective of time to expiry since the value of the American put is equal to its payoff. In contrast, $x > S^*(t)$ represents the \emph{continuation region} where the American put is worth more than its payoff and thus is more valuable to continue to hold the option. As we have mentioned in the introduction, the position of $S^*(t)$ (which divides the $x$ domain into the exercise and continuation regions) is unknown \emph{a priori} which adds another layer of difficulty to the option pricing problem.

@@

\section{Useful properties of the CDF of a standard normal variable}
\label{subsec:cdfproperties}
Several properties of the \textcolor{blue}{standard} cumulative normal distribution $N$ and its derivative $N'$ will also be required~\cite[pp. 235--239]{Jeff1995}, namely
	\begin{equation}
		\begin{split}
		N(x) = \fr{1}{\sqrt{2\pi}}\int_{-\infty}^x e^{-y^2/2} & \, \d y, \quad %= \fr{1}{2} + \fr{1}{2}\text{erf}\left(\fr{x}{\sqrt{2}}\right) \\
		N(-x) = 1 - N(x), \quad
		N'(x) = \fr{1}{\sqrt{2\pi}}e^{-x^2/2} \label{eqn:Nprime}, \\
		&N(\infty) = 1, \quad N(-\infty) = 0.
		\end{split}
	\end{equation}
We also require the bivariate (standard) normal CDF~\cite{Genz2004}
	\begin{equation}
		\label{eqn:N2}
		N_2(x,y;\rho) = \fr{1}{2\pi\sqrt{1-\rho^2}}\int_{-\infty}^x\int_{-\infty}^y e^{-(u^2-2\rho uv + v^2)/(2(1-\rho^2))} \, \d v \, \d u,
	\end{equation}
where $\rho \in (-1,1)$ . It is not difficult to show that	
	\begin{equation}
		\label{eqn:Nspecial}
		\begin{split}
		&N_2(x,\infty;\rho) = N(x), \quad N_2(\infty,y;\rho) = N(y),\\
		&N_2(x,-\infty;\rho) = N_2(-\infty,y;\rho) = 0, \\
		&N_2(-\infty,\infty;\rho) = N_2(\infty,-\infty;\rho) = 0, \quad N_2(\infty,\infty;\rho) = 1.
		\end{split}
	\end{equation}
\section{Lemmas and corollaries we will need}
The following lemmas and corollaries will also be of great use throughout this thesis:
\subsection{General lemmas}
	\begin{lemma}
		\label{lem:2}
	For $a > 0$ and $b \in \mathbb{R}$, we have
	\begin{equation*}
		\M^{-1}\left\{ e^{-b\xi/a}e^{\xi^2/(2a^2)} \right\} = aN'(a\log x + b).
	\end{equation*}
	\end{lemma}
\begin{proof}
	See Appendix A.1.
\end{proof}
	\begin{lemma}
		\label{lem:1}
		For $a_1, \, a_2 > 0$ and $b_1, \, b_2 \in \mathbb{R}$, we have
			\begin{align*}
				&\int_0^\infty \fr{1}{z}N'(a_1\log z + b_1)N'\left(a_2\log\left( 1/z \right) + b_2 \right) \, \d z =  \fr{1}{\sqrt{a_1^2 + a_2^2}}N'\left( \fr{a_1b_2 + a_2b_1}{\sqrt{a_1^2+a_2^2}} \right).
			\end{align*}
	\end{lemma}
	\begin{proof}
		See Appendix A.2.
	\end{proof}
	\begin{lemma}
		\label{lem:2b}
		For $a_1, \, a_2 > 0$, $b_1, \, b_2 \in \mathbb{R}$, and $c > 0$, \textcolor{blue}{it follows that}
		\begin{align*}
			&\int_c^\infty \fr{1}{z}N'(a_1\log z + b_1)N'\left(a_2\log\left( 1/z \right) + b_2 \right) \, \d z =  \fr{1}{\sqrt{a_1^2 + a_2^2}}N'\left( \fr{a_1b_2 + a_2b_1}{\sqrt{a_1^2+a_2^2}} \right)N(d),
		\end{align*}
		where
		$$
			d = \sqrt{a_1^2+a_2^2}\left( \log(1/c) + \fr{b_2}{a_2} - \fr{a_1\gamma}{a_1^2+a_2^2} \right), \quad
			\gamma = \fr{a_1b_2}{a_2} + b_1.
		$$
	\end{lemma}
	\begin{proof}
		See Appendix A.3.
	\end{proof}
